\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-25 paper.tex
Update keyword listing
Revise related work

\begin{IEEEkeywords}
    streaming data, crowd sensing, data marketplace, decentralization, blockchain
\end{IEEEkeywords}

@@

To address the inefficiency of the Blockchain, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency for the IoT industry based on a revolutionary distributed ledger technology, the \textbf{Tangle}, which enables zero-transaction. On top of that, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, is provided that allows transmission, access, and verification of an encrypted data stream over the Tangle. Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} that not only allows putting data on Tangle without any trusted cloud services, but also allows trading on Tangle where privacy and integrity meet with MAM. Nevertheless, the platform is centralized, where new devices require manual approval from the IOTA Foundation. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contracts which consist of providers, consumers and brokers. The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant is still forthcoming.

>>>>

\begin{IEEEkeywords}
    streaming data, data integrity, data marketplace, decentralization, blockchain
\end{IEEEkeywords}

@@

Targeting IoT industry, \textbf{IOTA}\cite{IOTAwhitepaper} is a cryptocurrency based on a revolutionary DLT, the \textbf{Tangle}, which has zero transaction fees and the potential for scalability. On top of Tangle network, \textbf{Masked Authenticated Messaging(MAM)}\cite{MAM}, allows transmission, access, and verification of an encrypted data stream. Based on Tangle and MAM, the IOTA Foundation launched a data marketplace\cite{IOTADataMarket} prototype that not only allows putting data on Tangle without any trusted cloud services, but also enables trading on Tangle where privacy and integrity meet with MAM. Nevertheless, the platform is centralized, where new devices require manual approval from the IOTA Foundation. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electrically noisy environment.

A 3-tier decentralized data marketplace architectural design\cite{3tierDataMarket} is known to reduce the burden of low-level devices, along with Ethereum smart contracts which consist of providers, consumers and brokers. The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant is still forthcoming.
